# Domain specific languages

## HTML

1.  __<span style="color:red">Q</span>__: The escaping rules for `<script>` and `<style>` tags are different: you
    don't want to escape angle brackets or ampersands, but you do want to
    escape `</script>` or `</style>`.  Adapt the code above to follow these
    rules.
    
    __<span style="color:green">A</span>__: 

    We modify the `tag` function to escape these special strings if and only if
    we are using the `<script>` or `<style>` tag. 

    ```{r, eval = FALSE}
    escape <- function(x, tag = NULL) UseMethod("escape")
    escape.html <- function(x, tag = NULL) x
    escape.character <- function(x, tag = NULL) {
      if (identical(tag, "script")) {
        x <- gsub("</script>", "&lt;/script&gt;", x)
      } else if (identical(tag, "style")) {
        x <- gsub("</style>", "&lt;/style&gt;", x)
      } else {
        x <- gsub("&", "&amp;", x)
        x <- gsub("<", "&lt;", x)
        x <- gsub(">", "&gt;", x)
      }

      html(x)
    }

    tag <- function(tag) {
      force(tag)
      function(...) {
        args <- list(...)
        attribs <- html_attributes(named(args))
        children <- unlist(escape(unnamed(args), tag = tag))

        html(paste0(
          "<", tag, attribs, ">",
          paste(children, collapse = ""),
          "</", tag, ">"
        ))
      }
    }
    ```

1.  __<span style="color:red">Q</span>__: The use of `...` for all functions has some big downsides. There's no
    input validation and there will be little information in the
    documentation or autocomplete about how they are used in the function. 
    Create a new function that, when given a named list of tags and their   
    attribute names (like below), creates functions which address this problem.

    ```{r, eval = FALSE}
    list(
      a = c("href"),
      img = c("src", "width", "height")
    )
    ```

    All tags should get `class` and `id` attributes.
    
    __<span style="color:green">A</span>__: 

    ```{r, eval = FALSE}
    generate_tags <- function(tags) {
      lapply(names(tags), function(tag) {
        force(tag)
        attribs <- union(tags[[tag]], c("class", "id"))
        fn <- function(...) {
          args <- do.call(list, as.list(match.call())[-1])
          attribs <- html_attributes(named(args))
          children <- unlist(escape(unnamed(args), tag = tag))

          html(paste0(
            "<", tag, attribs, ">",
            paste(children, collapse = ""),
            "</", tag, ">"
          ))
        }
        formals(fn) <- as.pairlist(stats::setNames(fn, attribs))
        fn
      })
    }
    ```

1. __<span style="color:red">Q</span>__: Currently the HTML doesn't look terribly pretty, and it's hard to see the
   structure. How could you adapt `tag()` to do indenting and formatting?
    
    __<span style="color:green">A</span>__: 

## LaTeX

1.  __<span style="color:red">Q</span>__: Add escaping. The special symbols that should be escaped by adding a backslash
    in front of them are `\`, `$`, and `%`. Just as with HTML, you'll need to 
    make sure you don't end up double-escaping. So you'll need to create a small 
    S3 class and then use that in function operators. That will also allow you 
    to embed arbitrary LaTeX if needed.
    
    __<span style="color:green">A</span>__: 

1.  __<span style="color:red">Q</span>__: Complete the DSL to support all the functions that `plotmath` supports.
    
    __<span style="color:green">A</span>__: 

1.  __<span style="color:red">Q</span>__: There's a repeating pattern in `latex_env()`: we take a character vector,
    do something to each piece, convert it to a list, and then convert the list 
    to an environment. Write a function that automates this task, and then rewrite
    `latex_env()`.
    
    __<span style="color:green">A</span>__: 

1.  __<span style="color:red">Q</span>__: Study the source code for `dplyr`. An important part of its structure is
    `partial_eval()` which helps manage expressions when some of the
    components refer to variables in the database while others refer to local R
    objects. Note that you could use very similar ideas if you needed to 
    translate small R expressions into other languages, like JavaScript or 
    Python.
    
    __<span style="color:green">A</span>__: 
